Thoughts on calibration

### 2013-12-06 articles/Report-Thoughts/thoughts.tex
Iterate peeling multiple times and subtract sources correctly

>>>>

This method works, but does not deal with ionospheric position shifting, and hence does in practice fail to do an accurate subtraction job when the source position are not found every short interval (2 min).

\section{Source position finding}
One can fit for a global (real) gain $g$ and two parameters $\Delta l$ and $\Delta m$ that describe the movement of the source. To do so, one calculates the optimization problem
\begin{equation}
 \min_{g,\Delta l,\Delta m} \epsilon(g,\Delta l,\Delta m),\hspace{1cm} g,\Delta l,\Delta m \in \mathcal{R}, g\approx 1, \Delta l\approx 0, \Delta m\approx 0
\end{equation}
where the error $\epsilon$ is defined as the squared magnitude of the difference between model and data:
\begin{equation}
 \epsilon(g,\Delta l,\Delta m) = \left| g e^{2\pi \left( u\Delta l + v\Delta m\right)} M(i) - V(i) \right|^2
\end{equation}
